peter_models

### 2024-12-06 peter_models.qmd
adding files
update chi-sq test, start modeling

---
title: "peter_EDA"
format: html
author: "Peter de Guzman"
editor: visual
---

Conducting EDA on the 2020 CMPS dataset for Research Question 1

@@

# Selecting Variables

# Cleaning Variables

# Analysis of Missing Data

# Save cleaned data

# Creating summary table

@@

# Fitting OLR Model

# Fitting MLR Model

>>>>

---
title: "peter_models"
format: html
author: "Peter de Guzman"
editor: visual
---

##

# Loading Packages

```{r}
library(tidyverse)
library(ordinal)
library(car)
library(brant)
library(MASS)
```

@@

```{r}
load("/Users/pdeguz01/Documents/git/Data/2020 CMPS/Output/2020cmps_clean.RData")
```

@@

```{r}
# Create a summary table for all categorical variables
variables <- c("Q29", "Q271", "S2_RACE_PRIME", "S3", "S3B", "S5_AGE", "S13", "S14", "S7", "Q21", "S2_M", "Q627", "Q628", "Q629R1", "Religion", "educ", "sex_orientation", "rural", "white", "race_recoded", "age_recoded")

# Chi-square tests for each variable
chi_square_results <- lapply(variables, function(var) {
  chisq.test(table(dataset_clean[[var]], dataset_clean$Q29))
})

# Print chi-square results
names(chi_square_results) <- variables
print(chi_square_results)
```

| Variable | Chi-Sq Test Statistic | Degrees of Freedom (df) | p-value |
|----|----|----|----|
| Q271 | 291.49 | 12 | \< 2.2e-16 |
| S2_RACE_PRIME | 291.12 | 21 | \< 2.2e-16 |
| S3 | 101.7 | 15 | 6.196e-15 |
| S3B | 296.35 | 9 | \< 2.2e-16 |
| S5_AGE | NaN | 18 | NA |
| S13 | 710.69 | 18 | \< 2.2e-16 |
| S14 | 196.79 | 12 | \< 2.2e-16 |
| S7 | 148.62 | 6 | \< 2.2e-16 |
| Q21 | 1284.1 | 9 | \< 2.2e-16 |
| S2_M | 6.0327 | 3 | 0.11 |
| Q627 | 246.82 | 3 | \< 2.2e-16 |
| Q628 | 9.0318 | 6 | 0.1718 |
| Q629R1 | 6.9533 | 3 | 0.0734 |
| Religion | 562.39 | 45 | \< 2.2e-16 |
| educ | 608.65 | 6 | \< 2.2e-16 |
| sex_orientation | 55.679 | 6 | 3.379e-10 |
| rural/urban&suburban | 83.719 | 3 | \< 2.2e-16 |
| white/non-white | 75.137 | 3 | 3.386e-16 |
| race_recoded | 276.36 | 18 | \< 2.2e-16 |
| age_recoded | 396.97 | 15 | \< 2.2e-16 |

## Takeaways from Chi-Square Test

# Fitting OLR Model
```{r}

```

## Interpretation

# Fitting MLR Model
```{r}

```

## Interpretation

# Fitting Proportional Odds Model
```{r}

```

## Interpretation
